### 2020-06-03 writeup/setup.tex
wip

We focus on the following problem that specializes the commonly used hard parameter sharing model (e.g. \cite{R17,MTDNN19}) to the linear regression setting \cite{WZR20}.
\begin{align}
	\label{eq_mtl}
	f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k B W_k - Y_k}^2,
\end{align}
where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
The linear layer $B$ provides a shared subspace for all tasks whereas each output layer $W_k$ fits the $k$-th task given the linear layer.
Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.

>>>>

We focus on the commonly used hard parameter sharing model for multi-task learning \cite{R17,MTDNN19}.
When specialized to the linear regression setting, the model consists of a linear layer $B\in\real^{p\times r}$ that is shared by all tasks and $t$ output layers $W_1, \dots, W_t$ that are in $\real^r$.
\begin{align}
	\label{eq_mtl}
	f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k B W_k - Y_k}^2,
\end{align}
where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.

Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
